Supplamental Appendix for ``Out-of-Sample Comparisons of Overfit Models''

### 2014-03-27 appendix.tex
Tweak intro to appendix

This appendix presents simulation results that accompany
\cite{Cal:14}. As in the main paper, these simulations were conducted
in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
packages. Graphs were produced in R using Lattice \citep{Sar:10} and
tikzDevice \citep{ShB:11:0.6.1}.

>>>>

This appendix presents simulation results that accompany
\citet{Cal:14}. The Monte Carlo here is exactly the same as presented
in \citet{Cal:14}, except that a recursive window is used. Please read
the original paper for further details.

\begin{itemize}

\item Figure 1 in this Appendix corresponds to Figure 3 in the
  original paper.
\item Figure 2 corresponds to Figure 4 in the paper.
\item Figure 3 corresponds to Figure 5 in the paper.
\item Figure 4 corresponds to Figure 6 in the paper.
\item Figure 5 corresponds to Figure 7 in the paper.

\end{itemize}
